Type Visualization for R

### 2020-06-19 paper/main.tex
paper: Background

% R background

% gradual typing background

% vis papers

\todo{
  We need to take a closer look at the papers we cite.
}

@@

@@

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{img/typevis.png}
 \caption{The main view of {\sc TypeVis}, with type flows on the left and the package hierarchy on the right.}
 \label{fig:typevis}
\end{figure*}

>>>>

R is a dynamically typed programming language widely used for
statistical computing. Unlike statically typed languages,
R programs do not contain type annotations
and never pass through a typechecker.
At run-time,
functions may called with values of arbitrary type,
and may return values of arbitrary type.\footnote{
  We use the word ``type'' to mean what others may call a ``type tag.''
  This is a run-time concept---we do not assume a static type system
  because there is none. Indeed, the goal is to help design one!
  A ``type signature'' in this context is one particular configuration
  of argument and return types a function is called with at run-time.
}

For statically typed languages, the type system is usually
an inseparable part of the language. Since they are designed
at the same time, the type system precedes any code written
in the language.
A gradual type system, by contrast,
permits the integration of static and dynamic typing.
Such a type system is capable of seamlessly mixing typed and untyped regions of code.
Often, a gradual type system is designed atop
an existing dynamically typed language.
Since many R programs already exist,
a successful gradual type system must be capable of
typechecking idiomatic R code.
{\sc TypeVis} aims to clarify how existing R programs
use types to assist in this task.
While this is our motivation, the visualization's use
is not necessarily limited to this application.
Anyone who has an interest in how the real R programs use types
may find it useful.

\todo{Prior work}

@@

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{img/typevis.png}
 \caption{The main view of {\sc TypeVis}, with type flows on the left and the package hierarchy on the right. Here, the {\tt length.unit} and {\tt valid.unit} functions from the {\tt grid} package are both selected and displayed simultaneously.}
 \label{fig:typevis}
\end{figure*}

@@
